Co-citations in context

### 2019-06-12 cocit_r.tex
fixed first para of Results section for the 4th time

To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions: (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%). We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area. These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.

>>>>

To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions (some publications qualify for more than one label): (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%). We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area. These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
